---
title: "plsr - Partial Least Squares Made Easy"
author: "Jan N. Schneider"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

plsr (read: "pleasure") is a package that provides simple to use Partial Least Squares Analysis.

It features:

* P-value calculation through permutation testing for latent variables 
* Backward and forward prediction 
* Various visualization functions for estimated latent variables


## Quick Start

The central function of the package is `pls()`. Given two matrices `X` and `Y` with arbitrary number of variables in columns and equal number of observations in rows this function will compute the latent variables that will maximize the covariance between `X` and `Y`.
For example, a plsr object can be calculated like so:
```{r, results="hide"}
library(plsr)
plsr_obj=pls(X=rating_data,Y=tracking_data,n_perm=1000,n_boot=10)
```  
## Inspecting Results

Resulting latent variables and their significances can be investigated using the generic functions `summary()` and `plot()`:
```{r}
summary(plsr_obj)
```

```
plot(plsr_obj)
```

```{r, echo=FALSE, fig.width = 3.5, fig.align = "center"}
plsr:::plot_perm_results(plsr_obj)
```

